Quantum Magic Games

### 2023-07-04 paper/main.tex
paper => typos

In this project, we will explore the Mermin-Peres magic square game
(hereinafter referred simply as magic square). The origins of this
game date back to the ninities. It was first described in the works of
Mermin~\cite{mermin:1990, mermin:1993} and of
Peres~\cite{peres:1990, peres:1997}. Their results provided (as per the title of
Mermin's review letter) a simplied proof for the Kochen-Specker
theorem~\cite{kochen:1967}. Later, in 2002, Aravind demonstrated how
to transform Mermin-Peres's proof of the Kochen-Specker theorem into a
proof of Bell's theorem~\cite{aravind:2002}. Bell's
theorem~\cite{bell:1964} shows the incompatibility of hidden variables
(i.e. determinism) and locality, and Kochen-Specker's theorem
demonstrates the conflicting nature of determinism and
noncontextuality (locality can be regarded as a special case of
contextuality). These sort of results may seem
challenging, but their descriptions can be greatly simplified by
modeling them as quantum games.  In particular, it is extremely easy
to show that there cannot be a classical solution to the the Magic
Square game, and to convince an observer that something ``magical''
(classically impossible) is happening in a successful implementation
of a quantum winnin strategy~\cite{brassard:2005}.

\paragraph{Outline of this paper.}
In Section~\ref{sec:magic-square}, we detail the intrinsics of the
magic square game, classical approaches and why it is impossible to
systematically win the game classically, how and why the quantum
strategy works, and how to implement it. We also briefly discuss how
the game translates to the proof of the incompatibility of a
noncontextual hidden-variable theory. Then, in
Section~\ref{sec:extending}, we describe a generalization of games
that follow the same style of the magic square game, given
by Arkhipov~\cite{arkhipov:2012}. Finally, section~\ref{sec:conc} concludes the
presentation.

@@

A magic square is a \(3 \times 3\) matrix whose entries are filled
with \(\pm 1\)'s. The product of every row of a magic square must be
\(+1\). Similarly, the product of every column of a magic square must
be \(-1\). Is impossible to satisfy these two properties at the same
time, hence the term \emph{magic}: such a matrix cannot exist. The
Magic Square game features two players, Alice and Bob, that must work
together to fill in entries of the \(3 \times 3\) table.  At the
beginning of the game, Alice and Bob are separated by a referee,
Charlie, so that communication between them is impossible. At each
round, Charlie assigns one row of the matrix at random to Alice, and
asks Alice to give him the entries to fill in that particular
row. After that, Charlie visits Bob and asks him to fill one column of
the table, which Charlie draws at random.  Bob does not know which row
Alice was assigned, and Alice does not know which colum Bob was
assigned. Alice and Bob win the round if their answers are valid,
i.e.\ the product of the row filled by Alice is \(+1\) and the product
of the column filled by Bob is \(-1\), and, in addition, the
intersection of the row and the column agrees (i.e. both answered
\(+1\) or both answered \(-1\)). Before the game starts, Alice and Bob
are allowed to communicate, so they can come up with an strategy.  For
example, they may prepare their answers for each row and column
beforehand, or they may decide to follow a probabilistic strategy.

@@

  {\renewcommand{\arraystretch}{2}
    \begin{figure}[H]
      \centering
      \begin{subfigure}[t]{0.475\textwidth}
        \[\begin{array}{|>{\quad\columncolor{gray!50}}c<{\quad}|*{2}{>{\quad}c<{\quad}|}}
            \hhline{---}
            -1 & -1 & +1 
            \\ \hhline{---}
            -1 & -1 & +1 
            \\ \hhline{---}
            -1 & -1 & +1 
            \\ \hhline{---}
          \end{array}\]
        \caption{Initially, Alice and Bob agree that Bob shall fill the
          first column with \(\{-1, -1, -1\}\). Based on this choice,
          Alice decides to fill all of her rows with
          \(\{-1, -1, +1\}\).}
      \end{subfigure}
      \hfill{}
      \begin{subfigure}[t]{0.475\textwidth}
        \[\begin{array}{|*{3}{>{\quad\columncolor{gray!50}}c<{\quad}|}}
            \hhline{---}
            -1 & -1 & \cellcolor{red!80!black!55}\pm 1
            \\ \hhline{---}
            -1 & -1 & +1
            \\ \hhline{---}
            -1 & -1 & +1
            \\ \hhline{---}
          \end{array}\]
        \caption{Bob has to fill the second column with \(-1\)'s, to match
          Alice's choice. He should also match Alice's choice for each
          cell of the third column, but he cannot, for the product of
          the column must be \(-1\).}
      \end{subfigure}
      \caption{One possible classical deterministic strategy for the Magic
        Square game. Following this predefined strategy, Alice and Bob
        lose when assigned, respectively, the first row and third column,
        but win in any other scenario. That is, their probability of
        winning a round is \(\nicefrac{8}{9}\). Gray cells are entries for
        which Alice's and Bob's choices agree.\label{fig:classical}}
    \end{figure}}
\end{tcbexample}

@@

It turns out that the best that they can do is to win
with probability \(\nicefrac{8}{9}\)

What if Alice and Bob decide for a probabilistic strategy? That is, Alice and
Bob each carry a coin. When assigned a row/column, they flip their
coins and fill the entries of the row/column based on the outcomes of
the coins. Can they do better? To randomly assign values to one row
(equivalently, one column) is essentially the same as randomly
selecting one of the \(2^{9}\) possible predefined \(3 \times 3\)
grids (including those matrices that would lead to invalid
answers). In other words, a probabilistic strategy for the Magic
Square game is one in which Alice and Bob randomly select a
deterministic strategy. Hence, no matter how lucky Alice and Bob are,
the probability of success of any strategy that they come up with is
bounded by the winning probability of the best deterministic strategy,
which is \(\nicefrac{8}{9}\). A formal proof is given in~\ref{xxx}
for any pseudo-telepathy game (i.e.\ games whose quantum strategies
exhibit this notion of pseudo-telapathy).

\subsection{Quantum Solution}
\label{sec:quantum-sol}
The quantum strategy for the Magic Square game consists of Alice and
Bob carrying entangled qubits with them. For each round, they need a
pair of qubits each. Then, when Charlie asks Alice (respectively Bob)
to fill the entries of the \(i\)-th row (respectively \(j\)-th
column), Alice measures her two qubits three times. The outcome of
each measurement gives the value for each cell (in practice, they do
not even need the third measurement, since they can determine the third
value from the first two). Key to this strategy is that the outcomes
of all possible measurements are \(\pm 1\). The initial, entangled state
is (subscripts \(A\) and \(B\) indicate, respectively,
Alice's and Bob's qubits)
\begin{equation}
  \ket{\psi} = \frac{1}{2}\left(
    \ket{00}_{A} \otimes \ket{00}_{B} + \ket{01}_{A} \otimes \ket{01}_{B} +
    \ket{10}_{A} \otimes \ket{10}_{B} + \ket{11}_{A} \otimes \ket{11}_{B}
  \right).
\end{equation}
Figure~\ref{fig:circuit-psi} shows the quantum circuit that can be
used to prepare the initial state \(\ket{\psi}\).

@@

As seen in Section~\ref{sec:classic-sol}, the \emph{magic} square is
called this way because, under classical assumptions, there is no such
a square: it is impossible to construct a \(3 \times 3\) matrix filled
with \(\pm 1\)'s, with the constraints that the product of every row
is \(+1\) and the product of every column is \(-1\). We can, however,
construct a ``quantum magic'' square. Figure~\ref{fig:quantum} shows
the \(3 \times 3\) grid that Alice and Bob can use to win the Magic
Square game systematically.  Notice that the eigenvalues of the
observables at each cell are \(\pm 1\). Furthermore, the product of
every row is \(+I\) and the product of every column is \(-I\).  The
quantum strategy works as follows: Alice measures all the observables
from the \(i\)-th row of the predefined matrix. She fills each cell
with the result of each measurement. Similarly, Bob measures all the
observables in the \(j\)-th column that was assigned to him, and fills
each cell of his cells with the outcomes of each
measurement. Example~\ref{ex:quantum-sol} depicts a round of the game.

{\renewcommand{\arraystretch}{2}
\begin{figure}[htbp] 
  \centering
  \[\begin{array}{|*{3}{>{\quad}c<{\quad}|}>{\quad}l<{\quad}}
      \hhline{---~}
      +I \otimes Z & +Z \otimes I & +Z \otimes Z & \prod = I \otimes I = I
      \\ \hhline{---~}
      +X \otimes I & +I \otimes X & +X \otimes X & \prod = I \otimes I = I
      \\ \hhline{---~}
      -X \otimes Z & -Z \otimes X & +Y \otimes Y & \prod = \ci{}I \otimes -\ci{}I = I
      \\ \hhline{---~}
      \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -\ci{}I \otimes -\ci{}I = -I}
    \end{array}\]
  \caption{Observables used by Alice and Bob to win the Magic Square game.\label{fig:quantum}}
\end{figure}}

@@

\subsection{Formal Proof}
To prove that the quantum solution indeed works, we must demonstrate
two fundamental properties. First, the product of the outcomes of the
three measurements on each row (equivalently, column) is equal to 1
(equiv. -1). Second, the outcome of Alice's measurement on the
intersection is always equal to the outcome of Bob's
measurement. Lemma~\ref{lem:product} formalizes the product property.

@@

\begin{table}[htbp]
  \centering
  \caption{Eigenvectors shared by the observables at each row of the quantum magic square.
    The eigenvectors were taken from~\ref{xxx}, adapting to the correct eigenvalues.}
  \label{tab:eigenv-rows}
  \begin{tabular}{c*{4}{>{\;\;}c}}
    \toprule
    & & Column 1 & Column 2 & Column 3 \\
    \midrule
    \multirow{2}{*}{Row 1} & \(+1\)
      & \ket{00}, \ket{10} & \ket{00}, \ket{01} & \ket{00}, \ket{11} \\
    & \(-1\)
      & \ket{01}, \ket{11} & \ket{10}, \ket{11} & \ket{01}, \ket{10} \\
    \midrule
    \multirow{4}{*}{Row 2} & \multirow{2}{*}{\(+1\)}
      & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} + \ket{11})\), \\ 
    & & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} - \ket{11})\)\phantom{,} 
                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} - \ket{11})\)\phantom{,} 
                            & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\)\phantom{,} \\[1.5mm]
    & \multirow{2}{*}{\(-1\)}
      & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} - \ket{11})\), \\ 
    & & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} - \ket{11})\)\phantom{,} 
                 & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} - \ket{11})\)\phantom{,} 
                            & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} - \ket{11})\)\phantom{,} \\
    \midrule
    \multirow{4}{*}{Row 3} & \multirow{2}{*}{\(+1\)}
      & \((\nicefrac{1}{2}) (\ket{01} - \ket{00} + \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{01} - \ket{00} + \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{01} - \ket{00} + \ket{10} + \ket{11})\), \\ 
    & & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} - \ket{11})\), \\[1.5mm]
    & \multirow{2}{*}{\(-1\)}
      & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} + \ket{11})\), \\
    & & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} - \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} - \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} + \ket{11})\), \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

In this project, we will explore the Mermin-Peres magic square game
(hereinafter referred simply as magic square). The origins of this
game date back to the ninities. It was first described in the works of
Mermin~\cite{mermin:1990, mermin:1993} and of
Peres~\cite{peres:1990, peres:1997}. Their results provided (as per the title of
Mermin's review letter) a simplied proof for the Kochen-Specker
theorem~\cite{kochen:1967}. Later, in 2002, Aravind demonstrated how
to transform Mermin-Peres's proof of the Kochen-Specker theorem into a
proof of Bell's theorem~\cite{aravind:2002}. Bell's
theorem~\cite{bell:1964} shows the incompatibility of hidden variables
(i.e. determinism) and locality, and Kochen-Specker's theorem
demonstrates the conflicting nature of determinism and
noncontextuality (locality can be regarded as a special case of
contextuality). These sort of results may seem
challenging, but their descriptions can be greatly simplified by
modeling them as quantum games.  In particular, it is extremely easy
to show that there cannot be a classical solution to the the magic
square game, and to convince an observer that something ``magical''
(classically impossible) is happening in a successful implementation
of a quantum winnin strategy~\cite{brassard:2005}.

\paragraph{Outline of this paper.}
In Section~\ref{sec:magic-square}, we detail the intrinsics of the
magic square game, classical approaches and why it is impossible to
systematically win the game classically, how and why the quantum
strategy works, and how to implement it. We also briefly discuss how
the game translates to the proof of incompatibility of a
noncontextual hidden-variable theory. Then, in
Section~\ref{sec:extending}, we describe a generalization of games
that follow the same style of the magic square game, given
by Arkhipov~\cite{arkhipov:2012}. Finally, Section~\ref{sec:conc} concludes the
presentation.

@@

A magic square is a \(3 \times 3\) matrix whose entries are filled
with \(\pm 1\)'s. The product of every row of a magic square must be
\(+1\). Similarly, the product of every column of a magic square must
be \(-1\). It is impossible to satisfy these two properties at the same
time, hence the term \emph{magic}: such a matrix cannot exist. The
magic square game features two players, Alice and Bob, that must work
together to fill in entries of the \(3 \times 3\) table.  At the
beginning of the game, Alice and Bob are separated by a referee,
Charlie, so that communication between them is impossible. At each
round, Charlie assigns one row of the matrix at random to Alice, and
asks Alice to give him the entries to fill in that particular
row. After that, Charlie visits Bob and asks him to fill one column of
the table, which Charlie draws at random.  Bob does not know which row
Alice was assigned, and Alice does not know which colum Bob was
assigned. Alice and Bob win the round if their answers are valid,
i.e.\ the product of the row filled by Alice is \(+1\) and the product
of the column filled by Bob is \(-1\), and, in addition, the
intersection of the row and the column agrees (i.e. both answered
\(+1\) or both answered \(-1\)). Before the game starts, Alice and Bob
are allowed to communicate, so they can come up with an strategy.  For
example, they may prepare their answers for each row and column
beforehand, or they may decide to follow a probabilistic strategy.

@@

  {\renewcommand{\arraystretch}{2}
    \begin{figure}[H]
      \centering
      \begin{subfigure}[t]{0.475\textwidth}
        \[\begin{array}{|>{\quad\columncolor{gray!50}}c<{\quad}|*{2}{>{\quad}c<{\quad}|}}
            \hhline{---}
            -1 & -1 & +1 
            \\ \hhline{---}
            -1 & -1 & +1 
            \\ \hhline{---}
            -1 & -1 & +1 
            \\ \hhline{---}
          \end{array}\]
        \caption{Initially, Alice and Bob agree that Bob shall fill the
          first column with \(\{-1, -1, -1\}\). Based on this choice,
          Alice decides to fill all of her rows with
          \(\{-1, -1, +1\}\).}
      \end{subfigure}
      \hfill{}
      \begin{subfigure}[t]{0.475\textwidth}
        \[\begin{array}{|*{3}{>{\quad\columncolor{gray!50}}c<{\quad}|}}
            \hhline{---}
            -1 & -1 & \cellcolor{red!80!black!55}\pm 1
            \\ \hhline{---}
            -1 & -1 & +1
            \\ \hhline{---}
            -1 & -1 & +1
            \\ \hhline{---}
          \end{array}\]
        \caption{Bob has to fill the second column with \(-1\)'s, to match
          Alice's choice. He should also match Alice's choice for each
          cell of the third column, but he cannot, for the product of
          the column must be \(-1\).}
      \end{subfigure}
      \caption{One possible classical deterministic strategy for the magic
        square game. Following this predefined strategy, Alice and Bob
        lose when assigned, respectively, the first row and third column,
        but win in any other scenario. That is, their probability of
        winning a round is \(\nicefrac{8}{9}\). Gray cells are entries for
        which Alice's and Bob's choices agree.\label{fig:classical}}
    \end{figure}}
\end{tcbexample}

@@

It turns out that the best that they can do is to win
with probability \(\nicefrac{8}{9}\).

What if Alice and Bob decide for a probabilistic strategy? That is, Alice and
Bob each carry a coin. When assigned a row/column, they flip their
coins and fill the entries of the row/column based on the outcomes of
the coins. Can they do better? To randomly assign values to one row
(equivalently, one column) is essentially the same as randomly
selecting one of the \(2^{9}\) possible predefined \(3 \times 3\)
grids (including those matrices that would lead to invalid
answers). In other words, a probabilistic strategy for the magic
square game is one in which Alice and Bob randomly select a
deterministic strategy. Hence, no matter how lucky Alice and Bob are,
the probability of success of any strategy that they come up with is
bounded by the winning probability of the best deterministic strategy,
which is \(\nicefrac{8}{9}\). A formal proof is given in~\cite{brassard:2005}
for any pseudo-telepathy game (i.e.\ games whose quantum strategies
exhibit this notion of pseudo-telapathy).

\subsection{Quantum Solution}
\label{sec:quantum-sol}
The quantum strategy for the magic square game consists of Alice and
Bob carrying entangled qubits with them. Then, when Charlie asks Alice
(respectively Bob) to fill the entries of the \(i\)-th row
(respectively \(j\)-th column), Alice measures her two qubits three
times. The outcome of each measurement gives the value for each cell
(in practice, they do not even need the third measurement, since they
can determine the third value from the first two). Key to this
strategy is that the outcomes of all possible measurements are
\(\pm 1\). The initial, entangled state is (subscripts \(A\) and \(B\)
indicate, respectively, Alice's and Bob's qubits)
\begin{equation*}
  \ket{\psi} = \frac{1}{2}\left(
    \ket{00}_{A} \otimes \ket{00}_{B} + \ket{01}_{A} \otimes \ket{01}_{B} +
    \ket{10}_{A} \otimes \ket{10}_{B} + \ket{11}_{A} \otimes \ket{11}_{B}
  \right).
\end{equation*}
Figure~\ref{fig:circuit-psi} shows the quantum circuit that can be
used to prepare the initial state \(\ket{\psi}\).

@@

As seen in Section~\ref{sec:classic-sol}, the \emph{magic} square is
called this way because, under classical assumptions, there is no such
a square: it is impossible to construct a \(3 \times 3\) matrix filled
with \(\pm 1\)'s, with the constraints that the product of every row
is \(+1\) and the product of every column is \(-1\). We can, however,
construct a ``quantum magic'' square. Figure~\ref{fig:quantum} shows
the \(3 \times 3\) grid that Alice and Bob can use to win the magic
square game systematically.  Notice that the eigenvalues of the
observables at each cell are \(\pm 1\). Furthermore, the product of
every row is \(+I\) and the product of every column is \(-I\).  The
quantum strategy works as follows: Alice measures all the observables
from the \(i\)-th row of the predefined matrix. She fills each cell
with the result of each measurement. Similarly, Bob measures all the
observables in the \(j\)-th column that was assigned to him, and fills
each of his cells with the outcomes of each
measurement. Example~\ref{ex:quantum-sol} depicts a round of the game.

{\renewcommand{\arraystretch}{2}
\begin{figure}[htbp] 
  \centering
  \[\begin{array}{|*{3}{>{\quad}c<{\quad}|}>{\quad}l<{\quad}}
      \hhline{---~}
      +I \otimes Z & +Z \otimes I & +Z \otimes Z & \prod = I \otimes I = I
      \\ \hhline{---~}
      +X \otimes I & +I \otimes X & +X \otimes X & \prod = I \otimes I = I
      \\ \hhline{---~}
      -X \otimes Z & -Z \otimes X & +Y \otimes Y & \prod = \ci{}I \otimes -\ci{}I = I
      \\ \hhline{---~}
      \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -\ci{}I \otimes -\ci{}I = -I}
    \end{array}\]
  \caption{Observables used by Alice and Bob to win the magic square game.\label{fig:quantum}}
\end{figure}}

@@

\subsection{Formal Proof}
To prove that the quantum solution indeed works, we must demonstrate
two fundamental properties. First, the product of the outcomes of the
three measurements on each row (equivalently, column) is equal to 1
(equiv. -1). Second, the outcome of Alice's measurement on the
intersection is always equal to the outcome of
Bob's. Lemma~\ref{lem:product} formalizes the product property.

@@

\begin{table}[t]
  \centering
  \caption{Eigenvectors shared by the observables at each row of the quantum magic square.
    The eigenvectors were taken from~\cite{breinig:online}, adapting to the correct eigenvalues.}
  \label{tab:eigenv-rows}
  \begin{tabular}{c*{4}{>{\;\;}c}}
    \toprule
    & & Column 0 & Column 1 & Column 2 \\
    \midrule
    \multirow{2}{*}{Row 0} & \(+1\)
      & \ket{00}, \ket{10} & \ket{00}, \ket{01} & \ket{00}, \ket{11} \\
    & \(-1\)
      & \ket{01}, \ket{11} & \ket{10}, \ket{11} & \ket{01}, \ket{10} \\
    \midrule
    \multirow{4}{*}{Row 1} & \multirow{2}{*}{\(+1\)}
      & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} + \ket{11})\), \\ 
    & & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} - \ket{11})\)\phantom{,} 
                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} - \ket{11})\)\phantom{,} 
                            & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\)\phantom{,} \\[1.5mm]
    & \multirow{2}{*}{\(-1\)}
      & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} - \ket{11})\), \\ 
    & & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} - \ket{11})\)\phantom{,} 
                 & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} - \ket{11})\)\phantom{,} 
                            & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} - \ket{11})\)\phantom{,} \\
    \midrule
    \multirow{4}{*}{Row 2} & \multirow{2}{*}{\(+1\)}
      & \((\nicefrac{1}{2}) (\ket{01} - \ket{00} + \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{01} - \ket{00} + \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{01} - \ket{00} + \ket{10} + \ket{11})\), \\ 
    & & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} - \ket{11})\), \\[1.5mm]
    & \multirow{2}{*}{\(-1\)}
      & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} + \ket{11})\), \\
    & & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} - \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} - \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} + \ket{11})\), \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}[t]
  \centering
  \caption{Eigenvectors shared by the observables at each column of the quantum magic square.
    The eigenvectors were taken from~\cite{breinig:online}, adapting to the correct eigenvalues.}
  \label{tab:eigenv-cols}
  \begin{tabular}{c*{4}{>{\;\;}c}}
    \toprule
    & & Row 0 & Row 1 & Row 2 \\
    \midrule
    \multirow{4}{*}{Column 0} & \multirow{2}{*}{\(+1\)}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{10})\),
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{10})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{10})\), \\
    & &  \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{10})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{11})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{11})\)\phantom{,} \\[1.5mm]
    & \multirow{2}{*}{\(-1\)}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{11})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{10})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{10})\), \\
    & & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{11})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{11})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{11})\)\phantom{,} \\
    \midrule
    \multirow{4}{*}{Column 1} & \multirow{2}{*}{\(+1\)}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{01})\),
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{01})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{01})\), \\
    & &  \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{01})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} + \ket{11})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} + \ket{11})\)\phantom{,} \\[1.5mm]
    & \multirow{2}{*}{\(-1\)}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} + \ket{11})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{01})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{01})\), \\
    & & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} - \ket{11})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} - \ket{11})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} - \ket{11})\)\phantom{,} \\
    \midrule
        \multirow{4}{*}{Column 2} & \multirow{2}{*}{\(+1\)}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{11})\),
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{11})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{10})\), \\
    & &  \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{11})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{10})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{11})\)\phantom{,} \\[1.5mm]
    & \multirow{2}{*}{\(-1\)}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{10})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{11})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{11})\), \\
    & & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{10})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{10})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{10})\)\phantom{,} \\
    \bottomrule
  \end{tabular}
\end{table}
